\documentclass[12pt,  letterpaper,  twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[margin=1.5cm]{geometry}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\title{End Sem Assignment CS384 -  Students who did not submit the feedback}
\author{Dr. Mayank Agarwal}
\date{Assignment Given: 22nd Nov 2021,\\ Deadline 23rd Nov 2021,  
	18:00 hrs. Submission: GitHub }

\begin{document}
	\maketitle  
	\textbf{Things to be kept in mind}\\
	\begin{enumerate} 
		\item Program will be checked for plagiarism.   
		
	\end{enumerate}

\textbf{Objective}	\\
Make a list of students who did not submit their feedback. Please refer the youtube video:
This is my link: \href{https://youtu.be/R3jzHfU7W84}{https://youtu.be/R3jzHfU7W84}.\\

You can download the video if you want 106 mb 

\href{https://drive.google.com/file/d/1iNm6pUZeXypx4mNe0DRjgdzZNpZ5Td57/view?usp=sharing}{https://drive.google.com/file/d/1iNm6pUZeXypx4mNe0DRjgdzZNpZ5Td57/view?usp=sharing}

Alternate link \\
\href{https://u.pcloud.link/publink/show?code=XZb9PIXZKxBwXbnqD3jEs4ikj9046jbFlJqk}{https://u.pcloud.link/publink/show?code=XZb9PIXZKxBwXbnqD3jEs4ikj9046jbFlJqk}

Alternate link \\
\href{https://filetransfer.io/data-package/yPdow6cT#link}{https://filetransfer.io/data-package/yPdow6cT\#link}


Alternate link \\
\href{https://www.transfernow.net/dl/20211121Rdtns0fT}{https://www.transfernow.net/dl/20211121Rdtns0fT}

Info about files

\textbf{course\_registered\_by\_all\_students.csv}\\
This contains the list of all courses for which he/she is registered.

\textbf{course\_master\_dont\_open\_in\_excel.csv}\\
This contains the LTP for every course. Ensure you open in libreoffice/notepad++/vscode/etc. DONT open in Excel of it will convert LTP to dates.

\textbf{course\_feedback\_submitted\_by\_students.csv}\\
This contains the feedback by students, this you will check which subject feedback is not submitted by students.

\textbf{course\_master\_for\_Backup.zip}\\
This contains the course\_master\_dont\_open\_in\_excel.csv, in case you opened in excel, replace that file with this one.

\textbf{studentinfo.csv}\\
personal info about student 

\textbf{Output File:}\\
course\_feedback\_remaining.xlsx   \textbf{Strict Excel file}.\\
This is self explanatory, for adding info in this file, you will need to take help of studentinfo.csv and course\_registered\_by\_all\_students.csv\\

\textbf{The algorithm.pdf explains the logic too along with the video.}
 
\end{document}